Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2012-08-06 paper.tex
Added to paper.  Looking good.

Recall the functions $G$, $h_1$ and $h_2$ defined in the statement of Theorem~\ref{thm:consistency}.  Observe that
\[
\expect G_L(\lambda) = \frac{\abs{P}}{L} h_1(\lambda) + \frac{\abs{D}}{L} h_2(\lambda)
\]
and since $\frac{\abs{P}}{L} \rightarrow p$ and $\frac{\abs{D}}{L} \rightarrow d$ as $L \rightarrow \infty$, then
\[
\lim_{L \rightarrow\infty} \expect G_L(\lambda) = G(\lambda) = p h_1(\lambda)   +  d h_2(\lambda).
\]
As is customary, let $(\Omega, \mathcal F, \prob)$ be the probability space over which the random variables $\{w_i\}$ are defined.  Let $A$ be the subset of the sample space $\Omega$ upon which $G(\hat{\lambda}_L) \rightarrow G(0)$ as $L\rightarrow\infty$.  Lemma~\ref{lem:convtoexpGlamL} shows that $\prob\{A\} = 1$.  Let $A'$ be the subset of the sample space upon which $\hat{\lambda}_L \rightarrow 0$ as $L\rightarrow \infty$.  Because $G$ is uniquely maximised at zero, it follows that $G(\hat{\lambda}_L) \rightarrow G(0)$ only if $\hat{\lambda}_L \rightarrow 0$ as $L \rightarrow\infty$. So $A \subseteq A'$ and therefore $\prob\{A'\} \geq \prob\{A\} = 1$.  Part one of Theorem~\ref{thm:consistency} follows.

@@

\begin{lemma}\label{lem:convtoexpGlamL} 
$G(\hat{\lambda}_L) \rightarrow G(0)$ almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
BLERG
% Lemma~\ref{lem:Zconunif} shows BLERG that 
% \[
% 0 \leq G(\hat{\lambda}_L) - G(0),
% \]
% and since $\hat{\lambda}_L$ is the maximiser of $G_L$ then
% \[ 
% 0 \leq G_L(0) - G_L(\hat{\lambda}_L).
% \]
% Adding both inequalities and taking appropriate absolute values gives
% \begin{align*}
% 0 &\leq G(\hat{\lambda}_L) - G(0) \\ 
% & \leq G(\hat{\lambda}_L) - G(0) + G_L(0) - G_L(\hat{\lambda}_L) \\
% & \leq |G(\hat{\lambda}_L) - G_L(\hat{\lambda}_L)| + |G_L(0) - G(0)|,
% \end{align*}
\end{IEEEproof}

@@

\begin{lemma}\label{lem:GLtoG0}
$G_L(\hat{\lambda}_L) \rightarrow G(0)$ almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
BLERG
\end{IEEEproof}

>>>>

Recall the functions $G$, $h_1$ and $h_2$ defined in the statement of Theorem~\ref{thm:consistency}.  Observe that
\[
\expect G_L(\lambda) = \frac{\abs{P}}{L} h_1(\lambda) + \frac{\abs{D}}{L} h_2(\lambda)
\]
and since $\frac{\abs{P}}{L} \rightarrow p$ and $\frac{\abs{D}}{L} \rightarrow d$ as $L \rightarrow \infty$, then
\[
\lim_{L \rightarrow\infty} \expect G_L(\lambda) = G(\lambda) = p h_1(\lambda)   +  d h_2(\lambda).
\]
As is customary, let $(\Omega, \mathcal F, \prob)$ be the probability space over which the random variables $\{w_i\}$ are defined.  Let $A$ be the subset of the sample space $\Omega$ upon which $\sabs{G(\hat{\lambda}_L)} \rightarrow \sabs{G(0)}$ as $L\rightarrow\infty$.  Lemma~\ref{lem:convtoexpGlamL} shows that $\prob\{A\} = 1$.  Let $A'$ be the subset of the sample space upon which $\hat{\lambda}_L \rightarrow 0$ as $L\rightarrow \infty$.  Because $\sabs{G(x)}$ is uniquely maximised at $x=0$, it follows that $\sabs{G(\hat{\lambda}_L)} \rightarrow \sabs{G(0)}$ only if $\hat{\lambda}_L \rightarrow 0$ as $L \rightarrow\infty$. So $A \subseteq A'$ and therefore $\prob\{A'\} \geq \prob\{A\} = 1$.  Part one of Theorem~\ref{thm:consistency} follows.

@@

\begin{lemma}\label{lem:convtoexpGlamL} 
$\sabs{G(\hat{\lambda}_L)} \rightarrow \sabs{G(0)}$ almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
Since $\sabs{G(x)}$ is uniquely maximised at $x=0$,
\[
0 \leq \sabs{G(\hat{\lambda}_L)} - \sabs{G(0)},
\]
and since $\hat{\lambda}_L$ is the maximiser of $\abs{G_L(x)}$,
\[ 
0 \leq \sabs{G_L(0)} - \sabs{G_L(\hat{\lambda}_L)}.
\]
Thus,
\begin{align*}
0 &\leq \sabs{G(\hat{\lambda}_L)} - \sabs{G(0)} \\ 
& \leq \sabs{G(\hat{\lambda}_L)} - \sabs{G(0)} + \sabs{G_L(0)} - \sabs{G_L(\hat{\lambda}_L)} \\
& \leq |G(\hat{\lambda}_L) - G_L(\hat{\lambda}_L)| + |G_L(0) - G(0)| \\
&\leq 2\sup_{x \in [-\pi, \pi)} \sabs{G(x) - G_L(x)},
\end{align*}
and the last line converges amost surely to zero by Lemma~\ref{lem:uniflawGGL}.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:GLtoG0}
$G_L(\hat{\lambda}_L) \rightarrow G(0)$ almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
By the triangle inequality,
\[
\sabs{G_L(\hat{\lambda}_L) - G(0)} \leq \sabs{G_L(\hat{\lambda}_L) - G(\hat{\lambda}_L)} + \sabs{G(\hat{\lambda}_L) - G(0)}.
\]
Now $\sabs{G_L(\hat{\lambda}_L) - G(\hat{\lambda}_L)} \rightarrow 0$ as $L \rightarrow \infty$ as a result of Lemma~\ref{lem:uniflawGGL}, and $\sabs{G(\hat{\lambda}_L) - G(0)} \rightarrow 0$ almost surely as $L \rightarrow \infty$ because $G$ is continuous and $\hat{\lambda}_L \rightarrow 0$ almost surely as $L \rightarrow \infty$.
\end{IEEEproof}

\begin{lemma}\label{lem:uniflawGGL}
The function $G_L$ converges almost surely and uniformly on $[-\pi, \pi)$ to the function $G$, that is,
\[
\sup_{x \in [-\pi, \pi)}\sabs{G_L(x) - G(x)} \rightarrow 0
\] 
almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
Put $T(x) = \expect G_L(x)$ and observe that
\begin{align*}
T(\lambda) - G(\lambda) &= \big(\tfrac{\abs{P}}{L} - p\big)h_1(\lambda) + \big(\tfrac{\abs{D}}{L} - d\big)h_2(\lambda) \\
&= o(1) h_1(\lambda) + o(1) h_2(\lambda)
\end{align*}
where $o(1)$ denotes a number converging to zero as $L \rightarrow \infty$.  Since $\sabs{h_1(\lambda)} \leq 1$ and $\sabs{h_2(\lambda)} \leq 1$ for all $\lambda \in [-\pi, \pi)$, then $\sup_{\lambda \in [-\pi, \pi)}\sabs{T(\lambda) - G(\lambda)} \rightarrow 0$ as $L\rightarrow \infty$.  Now
\begin{align*}
\sup_{\lambda \in [-\pi, \pi)}&\sabs{G_L(\lambda) - G(\lambda)} \\
&\leq \sup_{\lambda \in [-\pi, \pi)}\sabs{G_L(\lambda) - T(\lambda) + T(\lambda) - G(\lambda)} \\
&\leq \sup_{\lambda \in [-\pi, \pi)}\sabs{G_L(\lambda) - T(\lambda)} +  \sup_{\lambda \in [-\pi, \pi)}\sabs{T(\lambda) - G(\lambda)}
\end{align*}
and Lemma~\ref{lem:uniflawTGL} shows that $\sup_{\lambda \in [-\pi, \pi)}\sabs{G_L(\lambda) - T(\lambda)} \rightarrow 0$ as $L\rightarrow \infty$.
\end{IEEEproof}

\begin{lemma}\label{lem:uniflawTGL} 
Put $T(x) = \expect G_L(x)$, then
\[
\sup_{x \in [-\pi, \pi)}\sabs{G_L(x) - T(x)} \rightarrow 0
\] 
almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
BLERG
\end{IEEEproof}
